\vspace{2cm} \LARGE \bf Seasonal influenza circulation patterns and projections for 2017-2018

### 2017-02-24 auspice/reports/tex/feb-2017.tex
Fix figure legend.

\begin{figure}[h!]
	\centering
	\includegraphics[width=1.0\textwidth]{../figures/feb-2017/H3N2_tree_titer_model.png}
	\caption{\textbf{H3N2 phylogeny colored by antigenicity.}
	The left panel shows individual HI measurements of viruses against serum from A/HongKong/5738/2014.
	Cooler color indicates great antigenic similarity (less titer drop going from homologous to heterologous titers).
	The right panel shows model estimates of antigenic divergence from the root of the phylogeny.
	These estimates combine HI measurements from many different sera.
	Crick data is current through Sep 2016 and CDC data is current through Feb 2017.
	}
	\label{H3N2_tree_titer_model}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=1.0\textwidth]{../figures/feb-2017/H3N2_tree_titer_model.png}
	\caption{\textbf{H3N2 phylogeny colored by antigenicity.}
	Each panel shows model estimates of antigenic divergence relative to serum from A/HongKong/5738/2014.
	Cooler color indicates greater antigenic similarity (less titer drop going from homologous to heterologous titers).
	These estimates combine HI measurements from many different sera.
	The left panel uses HI data from the Crick Institute in London, the center panel uses HI data from the CDC in Atlanta and the right panel uses FRA data from the CDC.
	Crick data is current through Sep 2016 and CDC data is current through Feb 2017.
	}
	\label{H3N2_tree_titer_model}
\end{figure}
